Modelling the co-evolution of trade and culture in the Roman market

### 2015-04-08 article.tex
graphs with G=3 & n=500

Several studies focus on the biases that affect the transmission of cultural traits, including the relevance of intrinsic traits and frequency dependence properties. These analysis often compare evidence against neutral models~\shortcite{neiman_stylistic_1995}. They assume that traits do not affect the fitness of the individual that acquire it; within this context its transmission is unbiased, and its success will depend on its popularity amongst the rest of individuals. This neutral model generates a distinctive pattern of frequency distribution of traits, identified as a power law. It can be replicated with a simple random copying transmission mechanism~\shortcite{bentley_random_2004}: an individual will copy the traits of a randomly chosen individual with a given probability. This copy can potentially introduce some errors in the acquired trait, which account for innovation processes. The individual will in turn continue to spread these cultural traits which will be further adopted by other individuals. This basic model can be enriched by several additional processes both in the innovation~\shortcite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmission~\shortcite{heyes_social_1994,henrich_evolution_2003}. Unbiased transmission works as a baseline for identifying frequency-dependent biases: if evidence has higher tendency to copy the most common trait is is known as conformism, while the opposite is defined as anti-conformism.

@@

\begin{equation}
	 W^o=(w_g^o = v_g^o,w_k^o= \frac{v_k^o}{v_g^o}) 
	 W^r=(w_k^r = v_k^r,w_g^r= \frac{v_g^r}{v_k^r}) 
	 \label{eq:trade}
\end{equation}

@@

\begin{table}
\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
Parameter & Value \\
\midrule
Number of goods & 4 \\
Number of agents & 800 \\
Mutation probability & .004 \\
Innovation probability & .001\\
CulturalStep &  10 \\
TradeThreshold & 100  \\
TimeSteps & 200000 \\
\bottomrule
\end{tabular}
\caption{Table of parameters}\label{tab:parameters}
\end{center}
\end{table}

@@

\begin{figure}[!hbp]
	\begin{center}
		\includegraphics[width=6cm]{img/allmuRandMaxN250.pdf}
		\includegraphics[width=6cm]{img/allmuRandMaxN500.pdf}
	\end{center}
	\caption{Distribution of frequencies depending on the $\mu$ parameter with 250 agents (left) and 500 agents (right)\label{fig:allMutation}}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=6cm]{img/2SetupDistrib.pdf}
	\end{center}
	\caption{Frequency distribution for the neutral and the trade models}
	\label{fig:2setDi}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{tabular}{ c c}
		 Neutral Model & Trade Model \\
		 \includegraphics[width=5cm]{img/ScoreEvolutionForRandom-G2N500.pdf}
		 & \includegraphics[width=5cm]{img/ScoreEvolutionForTrade-G2N500.pdf}

	\end{tabular}
	\caption{Evolution of the score within the two different models.}%%
	\label{fig:scoreEvol}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=7cm]{img/ClearingPriceDistanceEvolutionForTrade-G2N500.pdf}
	\end{center}
	\caption{Evolution of the mean difference for each good of the estimated value $v_g$ and its optimal value as given by \ref{eq:optimum}. Means computed for 100 run and 2 goods. }
	\label{fig:ratioEvol}
\end{figure}

>>>>

Several studies focus on the biases that affect the transmission of cultural traits, including the relevance of intrinsic traits and frequency dependence properties. These analysis often compare evidence against neutral models~\shortcite{neiman_stylistic_1995}. They assume that traits do not affect the fitness of the individual that acquire it; within this context its transmission is unbiased, and its success will depend on its popularity amongst the rest of individuals. This neutral model generates a distinctive pattern of frequency distribution of traits, identified as a power law. It can be replicated with a simple random copying transmission mechanism~\shortcite{bentley_random_2004}: an individual will copy the traits of a randomly chosen individual with a given probability. This copy can potentially introduce some errors in the acquired trait, which account for innovation processes. The individual will in turn continue to spread these cultural traits which will be further adopted by other individuals. This basic model can be enriched by several additional processes both in the innovation~\shortcite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmissio~\shortcite{heyes_social_1994,henrich_evolution_2003}. Unbiased transmission works as a baseline for identifying frequency-dependent biases: if evidence has higher tendendy to copy the most common trait is is known as conformism, while the opposite is defined as anti-conformism.

@@

\begin{equation}
	 W^o=(w_g^o = v_g^o,w_k^o= \frac{v_k^o}{v_g^o}), \quad
	 W^r=(w_k^r = v_k^r,w_g^r= \frac{v_g^r}{v_k^r}) 
	 \label{eq:trade}
\end{equation}

@@

\begin{table}
\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
Parameter & Value \\
\midrule
Number of goods & 3 \\
Number of agents & 500 \\
Mutation probability & .004 \\
Innovation probability & .001\\
CulturalStep &  10 \\
TradeThreshold & 100  \\
TimeSteps & 10000 \\
\bottomrule
\end{tabular}
\caption{Table of parameters}\label{tab:parameters}
\end{center}
\end{table}

@@

\begin{figure}[!hbp]
	\begin{center}
		\includegraphics[width=6cm]{img/allmuRandMaxN250.pdf}
		\includegraphics[width=6cm]{img/allmuRandMaxN500.pdf}
	\end{center}
	\caption{Distribution of frequencies depending on the $\mu$ parameter with 250 agents (left) and 500 agents (right). Each plot is the mean obtenaid for 100 runs.\label{fig:allMutation}}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=6cm]{img/2SetupDistrib.pdf}
	\end{center}
	\caption{Frequency distribution for the neutral and the trade models. Each points represent the mean for 100 runs.}
	\label{fig:2setDi}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{tabular}{ c c}
		 Neutral Model & Trade Model \\
		 \includegraphics[width=5cm]{img/ScoreEvolutionForRandom-G3N500.pdf}
		 & \includegraphics[width=5cm]{img/ScoreEvolutionForTrade-G3N500.pdf}

	\end{tabular}
	\caption{Evolution of the score within the two different models for two typical run with 500 agents and 3 goods evolving during 10000 timestep}%%
	\label{fig:scoreEvol}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=7cm]{img/ClearingPriceDistanceEvolutionForTrade-G3N500.pdf}
	\end{center}
	\caption{Evolution of the mean of the difference between the estimated value $v_g$ and the optimal value $\tilde{v}_g$ (as calculated with the equations~\ref{eq:optimum}) of the good $g$. This mean is plotted for 100 runs with 3 goods and 500 agents.}
	\label{fig:ratioEvol}
\end{figure}
